---
title: "Victim intoxicated cases"
subtitle: "Internal only"
author: "MaryJo Webster"
date:  "Last updated: `r Sys.Date()`"
output:
  html_document: 
    #toc: true
    #to_depth: 1
    #toc_float: true
    theme: flatly
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, cache=FALSE)

#URL FOR THIS PAGE: http://strib-data-internal.s3-us-west-1.amazonaws.com/projects/rape/liquor.html
```

```{r, code=readLines("load_clean_data.R"), echo=FALSE, warning=FALSE, message=FALSE}

```



```{r}

rape_intox <- rape %>% filter(victimintoxicated!="Unknown") %>% mutate(intoxflag=case_when(victimintoxicated=="Yes"~"Intoxicated", victimintoxicated=="No"~"Not intoxicated"))

intox <-  rape_intox %>% group_by(intoxflag) %>% summarise(count=n()) %>% mutate(pct = round((count/sum(count))*100,0)) 




#this assigns the first column of the cases data frame as the "names" for the waffle chart and assigns the third column as the "values"
intox_waffledata <-  data.frame(names=intox[, 1],vals=intox[,3])

#this makes the waffle chart. Can also add other labels, like source, etc

#waffle(intox_waffledata, rows=10, size=0.5, colors=c("#006666", "#33cc33"), title="Share of cases with intoxicated victims")

```



#Comparing police actions
Cases where victim was intoxicated versus those where victim was not

```{r}
intox_investigate <-  rape_intox  %>%  group_by(intoxflag, investigatorsassigned) %>% summarise(count=n()) 


intox_investigate <- 	intox_investigate %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(investigatorsassigned=="Yes")


intox_investigate_chart <- 	ggplot(intox_investigate, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_investigate$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Cases assigned to investigators",
       x=NULL,
       y=NULL)

plot(intox_investigate_chart)

```




```{r}
intox_vinterview <-  rape_intox %>%  group_by(intoxflag, victiminterviewed) %>% summarise(count=n()) 


intox_vinterview <- 	intox_vinterview %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(victiminterviewed=="Yes")


intox_vinterview_chart <- 	ggplot(intox_vinterview, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_vinterview$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Investigtor interviewed victim",
       x=NULL,
       y=NULL)

plot(intox_vinterview_chart)
```




```{r}
intox_sinterview <-  rape_intox %>% filter(suspectflag=="Named suspect") %>%  group_by(intoxflag, suspectinterviewed) %>% summarise(count=n()) 


intox_sinterview <- 	intox_sinterview %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(suspectinterviewed=="Yes")


intox_sinterview_chart <- 	ggplot(intox_sinterview, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_sinterview$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Investigtor interviewed named suspect",
       subtitle="Only cases with named suspect",
       x=NULL,
       y=NULL)

plot(intox_sinterview_chart)
```



```{r}
intox_evidence <-  rape_intox %>% filter(delay=="no delay") %>%  group_by(intoxflag, evidence2) %>% summarise(count=n()) 


intox_evidence <- 	intox_evidence %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(evidence2=="All collected")


intox_evidence_chart <- 	ggplot(intox_evidence, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_evidence$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "All potential evidence collected",
       subtitle="Only cases with no reporting delay",
       x=NULL,
       y=NULL)

plot(intox_evidence_chart)
```




```{r}
intox_witness <-  rape_intox %>%   group_by(intoxflag, witness2) %>% summarise(count=n()) 


intox_witness <- 	intox_witness %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(witness2=="All witnesses interviewed")


intox_witness_chart <- 	ggplot(intox_witness, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_witness$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "All potential witnesses interviewed",
       x=NULL,
       y=NULL)

plot(intox_witness_chart)

#rape_intox %>% group_by(witness2) %>% summarise(count=n())
```


#When victim cooperates

```{r}
intox_investigate <-  rape_intox %>% filter(victiminvolve=="Cooperated throughout") %>%  group_by(intoxflag, investigatorsassigned) %>% summarise(count=n()) 


intox_investigate <- 	intox_investigate %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(investigatorsassigned=="Yes")


intox_investigate_chart <- 	ggplot(intox_investigate, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_investigate$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Cases assigned to investigators",
       subtitle="Victim involved throughout",
       x=NULL,
       y=NULL)

plot(intox_investigate_chart)

```




```{r}
intox_vinterview <-  rape_intox %>% filter(victiminvolve=="Cooperated throughout") %>% group_by(intoxflag, victiminterviewed) %>% summarise(count=n()) 


intox_vinterview <- 	intox_vinterview %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(victiminterviewed=="Yes")


intox_vinterview_chart <- 	ggplot(intox_vinterview, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_vinterview$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Investigtor interviewed victim",
       subtitle="Victim involved throughout",
       x=NULL,
       y=NULL)

plot(intox_vinterview_chart)
```




```{r}
intox_sinterview <-  rape_intox %>% filter(suspectflag=="Named suspect", victiminvolve=="Cooperated throughout") %>%  group_by(intoxflag, suspectinterviewed) %>% summarise(count=n()) 


intox_sinterview <- 	intox_sinterview %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(suspectinterviewed=="Yes")


intox_sinterview_chart <- 	ggplot(intox_sinterview, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_sinterview$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Investigtor interviewed named suspect",
       subtitle="Only cases with named suspect; victim involved throughout",
       x=NULL,
       y=NULL)

plot(intox_sinterview_chart)
```



```{r}
intox_evidence <-  rape_intox %>% filter(delay=="no delay", victiminvolve=="Cooperated throughout") %>%  group_by(intoxflag, evidence2) %>% summarise(count=n()) 


intox_evidence <- 	intox_evidence %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(evidence2=="All collected")


intox_evidence_chart <- 	ggplot(intox_evidence, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_evidence$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "All potential evidence collected",
       subtitle="No delay; victim involved",
       x=NULL,
       y=NULL)

plot(intox_evidence_chart)
```




```{r}
intox_witness <-  rape_intox %>% filter(victiminvolve=="Cooperated throughout") %>%  group_by(intoxflag, witness2) %>% summarise(count=n()) 


intox_witness <- 	intox_witness %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(witness2=="All witnesses interviewed")


intox_witness_chart <- 	ggplot(intox_witness, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_witness$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "All potential witnesses interviewed",
       subtitle="Victim involved throughout",
       x=NULL,
       y=NULL)

plot(intox_witness_chart)

#rape_intox %>% group_by(witness2) %>% summarise(count=n())
```

#Comparing outcomes
Cases where victim was intoxicated versus those where victim was not

```{r}
intox_involve <-  rape_intox %>%  group_by(intoxflag, victiminvolve) %>% summarise(count=n()) 


intox_involve <- 	intox_involve %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(victiminvolve=="Cooperated throughout")


intox_involve_chart <- 	ggplot(intox_involve, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_involve$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Victim involved throughout",
       x=NULL,
       y=NULL)

plot(intox_involve_chart)
```

```{r}
intox_pros <-  rape_intox %>%  group_by(intoxflag, sentforprosecution) %>% summarise(count=n()) 


intox_pros <- 	intox_pros %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(sentforprosecution=="Yes")


intox_pros_chart <- 	ggplot(intox_pros, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_pros$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Sent for prosecution",
       x=NULL,
       y=NULL)

plot(intox_pros_chart)
```


```{r}
intox_charge <-  rape_intox %>%  group_by(intoxflag, chargesfiled) %>% summarise(count=n()) 


intox_charge <- 	intox_charge %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(chargesfiled=="Yes")


intox_charge_chart <- 	ggplot(intox_charge, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_charge$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Charges filed",
       x=NULL,
       y=NULL)

plot(intox_charge_chart)
```



```{r}
intox_conv <-  rape_intox %>%  group_by(intoxflag, conviction) %>% summarise(count=n()) 


intox_conv <- 	intox_conv %>% group_by(intoxflag) %>%
	mutate(pct = (count/sum(count)))	%>%
	filter(conviction=="Yes")


intox_conv_chart <- 	ggplot(intox_conv, aes(x = intoxflag, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((intox_conv$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Results in conviction",
       x=NULL,
       y=NULL)

plot(intox_conv_chart)
```


#Older charts

Pct of cases involving intoxicated victim
```{r}
rape%>% tabyl(legaltype, victimintoxicated)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```




Victim involvement

Victims who were intoxicated are more likely to withdraw

```{r}
rape %>% 
  tabyl(victimintoxicated, victiminvolve)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  #adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```





Victim involvement by legal type<br>
Only cases with intoxicated victim

```{r}
rape %>% 
  filter(victimintoxicated=="Yes") %>% 
  tabyl(legaltype, victiminvolve)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  #adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



Sent to investigators by victim intoxication

```{r}
rape%>%
  tabyl(victimintoxicated, investigatorsassigned)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  #adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```




Sent for prosecution by victim intoxication


```{r}
rape %>% 
  filter(victiminvolve=="Cooperated throughout") %>% 
  tabyl(victimintoxicated, sentforprosecution)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


Charges filed by victim intoxication


```{r}
rape %>% tabyl(victimintoxicated, chargesfiled)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```




Conviction rates by victim intoxication<br>
victim intoxicated=yes


```{r intoxcases, echo=FALSE}

rape %>% tabyl(victimintoxicated, conviction)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


Declined cases<br>
victim intoxicated=yes<br>
sent for prosecution = yes


```{r declinedsuspectcolor, echo=FALSE}
rape %>% filter(sentforprosecution=="Yes")%>%  tabyl(victimintoxicated, declinedcase)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



Potential evidence collected by victim intoxication<br>
Where no delay in reporting<br>


```{r}

rape%>%filter(delay=="no delay", victiminvolve=="Cooperated throughout") %>% tabyl(victimintoxicated, evidence2)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

Potential witnesses interviewed by victim intoxication



```{r}
rape%>% 
  filter(victiminvolve=="Cooperated throughout") %>% 
  tabyl(victimintoxicated, witness2)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



Victim interviewed by victim intoxication

```{r}
rape%>% 
  filter(victiminvolve=="Cooperated throughout") %>% 
  tabyl(victimintoxicated, victiminterviewed)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

Suspect interviewed by victim intoxication<br>
Where there is a named suspect<br>

```{r}
rape%>%filter(suspectflag=="Named suspect", victiminvolve=="Cooperated throughout") %>% tabyl(victimintoxicated, suspectinterviewed)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

Suspect arrested by victim intoxication<br>
Only cases with a named suspect<br>


```{r}
rape %>% filter(suspectflag=="Named suspect", victiminvolve=="Cooperated throughout") %>% tabyl(victimintoxicated,suspectarrested)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```












```{r movetoS3, echo=FALSE, eval=FALSE, results="hide"}


#rmarkdown::render("rape2018.Rmd")


# specify keys as environment variables

Sys.setenv("AWS_ACCESS_KEY_ID" =  rstudioapi::askForPassword("AWS_ACCESS_KEY_ID"),

           "AWS_SECRET_ACCESS_KEY" = rstudioapi::askForPassword("AWS_SECRET_ACCESS_KEY"))

get_bucket("strib-data-internal")


put_object(file = "liquor.html", object = "projects/rape/liquor.html", bucket = "strib-data-internal")

put_object(file = "liquor.html", object = "projects/rape/liquor.html", bucket = "strib-data-internal", acl=c("public-read"))


```
