---
title: "Rape project 2018 - weekly analysis"
subtitle: "Internal only"
author: "MaryJo Webster"
date:  "Last updated: `r Sys.Date()`"
output:
  html_document: 
    toc: true
    to_depth: 1
    toc_float: true
    theme: flatly
    


#This file contains the bulk of the analysis work from Denied Justice
#However, the key findings that were used in publication are most easily found in highlights.rmd


---


```{r setup, include=FALSE}
#need to make sure cache is set to false; otherwise it won't detect that we have new data
#when cache is set to true it only rebuilds new code (ignores situations where code is unchanged but there's new #underlying data)
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, cache=FALSE)


```

```{r, code=readLines("load_clean_data.R"), echo=FALSE, warning=FALSE, message=FALSE}
#this is needed for loading data
```




```{r dupsearch, include=FALSE, eval=FALSE}
#look for duplicates
#rape %>% group_by(casenumber) %>% summarise(count=n()) %>% arrange(desc(count))
```

Other pages: 
<a href="http://strib-data-public.s3-us-west-1.amazonaws.com/projects/rape/highlights.html">Highlights for sources</a><br>

<a href="http://strib-data-internal.s3-us-west-1.amazonaws.com/projects/rape/liquor.html">Analysis of cases where victim was intoxicated</a>

http://strib-data-public.s3-us-west-1.amazonaws.com/projects/rape/top4.html



#Top-level numbers

#Number of cases reviewed
```{r}
rape %>% group_by(department_collapse) %>% summarise(count=n()) %>%arrange(desc(count)) %>%  rename(dept=department_collapse) %>% adorn_totals("row") %>%  kable("html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```





##By department

```{r numbydepartment, echo=FALSE, strip.white=TRUE}
#number of cases by department
dept_num_cases <- rape %>%  group_by(department) %>% summarise(count=n()) %>% arrange(desc(count))



datatable(dept_num_cases)



```

##Pct of cases with an arrest
Percentage of cases with a named suspect that result in arrest

```{r}
rape%>% tabyl(suspectflag , suspectarrested)%>%
    adorn_totals("col") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
   adorn_ns() %>% 
   adorn_title("top")%>%
  knitr::kable("html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



##Victim involvement-Sent for prosecution
Cases with a victim who cooperates throughout the case are far more likely to be sent for prosecution

```{r}
rape%>% tabyl(victiminvolve, sentforprosecution)%>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")

```






##Cases assigned to an investigator
```{r}
rape%>%tabyl(department, investigatorsassigned)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  #rename(dept=department_collapse)%>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



##Cases by legal type

```{r legaltype, echo=FALSE}
rape%>%
  tabyl(casetype, legaltype)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  #rename(dept=department_collapse)%>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

#Acquaintance vs STranger
```{r}
rape %>% filter(conviction=='Yes') %>% group_by(casetype) %>% summarise(count=n()) %>% mutate(pct=count/sum(count)) %>% 
    knitr::kable("html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

##Conviction by case type

```{r}
rape%>% tabyl(casetype , conviction)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
   adorn_ns() %>% 
   adorn_title("top")%>%
  knitr::kable("html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



##Pct of cases involving suspect of color

```{r}
suspectcolor <- rape %>% filter(suspectflag=="Named suspect" | suspectflag=="Partial name") %>% 
  group_by(suspect_personofcolor) %>%
  summarise(count=n()) %>%
  mutate(pct=count/sum(count))

suspectcolor$pct_d <-  percent_format()(suspectcolor$pct)

suspectcolor %>% select(suspect_personofcolor, count, pct_d) %>% kable("html") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


##Declined cases

sent for prosecution = yes


```{r declinedbycasetype, echo=FALSE}

rape %>%filter(sentforprosecution=="Yes")%>%   tabyl(department_collapse, declinedcase)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>%
  adorn_title("combined")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```




##Reporting delays

```{r delays, echo=FALSE}


rape %>% tabyl(delay, conviction)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("combined")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



##Arrest rates
Only cases with a named suspect

```{r arrest, echo=FALSE}


rape %>% filter(suspectflag=="Named suspect") %>% tabyl(casetype,suspectarrested)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
adorn_ns() %>% 
  adorn_title("combined")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
      
```


##Charges filed
Percentage of all cases where charges were filed

```{r chargesfiled, echo=FALSE}
rape%>%tabyl(department_collapse, chargesfiled)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

Charges filed by case type

```{r}
rape%>%tabyl(casetype, chargesfiled)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```




## Victim involvement rates <br>
Percentage of cases where victim drop outs, by department

```{r victimimvolve,echo=FALSE}
rape%>%tabyl(department_collapse, victiminvolve)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



##Conviction rates

```{r convict_graphic, echo=FALSE}

convict_graphic <- rape%>%tabyl(department_collapse, conviction)%>%
    adorn_totals("col") %>%
mutate(pct=(Yes/Total))



convict_chart <- ggplot(convict_graphic, aes(x = department_collapse, y = pct)) + 
  geom_bar(stat = "identity", color="black", fill="#2956B2") +
  geom_text(stat="identity", nudge_x=0, nudge_y=-.02,label=paste0(round((convict_graphic$pct)*100,0),"%"))+
    coord_flip() +
  scale_y_continuous(labels = percent, limits=c(0,.4))+
  labs(title = "Conviction rates", 
       caption = "Star Tribune graphic by MaryJo Webster",
       x="Department",
       y="Pct of cases resulting in conviction")

plot(convict_chart)

```





Conviction by case type:

```{r convictcasetype, echo=FALSE}
convict_case_type <- rape %>% tabyl(casetype, conviction) %>% 
adorn_totals("col") %>%
  mutate(pct=(Yes/Total))

convict_casetype_chart <- ggplot(convict_case_type, aes(x = casetype, y = pct)) + 
  geom_bar(stat = "identity", color="black", fill="#2956B2") +
  geom_text(stat="identity", nudge_x=0, nudge_y=-.02,label=paste0(round((convict_case_type$pct)*100,0),"%"))+
    coord_flip() +
  scale_y_continuous(labels = percent, limits=c(0,.4))+
 labs(title = "Conviction rates by case type", 
      caption = "Star Tribune graphic by MaryJo Webster",
     x="Case type",
      y="Pct of cases resulting in conviction")

plot(convict_casetype_chart)

```
Conviction By Department<br>
Percentage of cases resulting in conviction
```{r}
dept_conviction_rate2 <-   rape %>% 
  group_by(department, conviction) %>% summarise(count=n())

dcast_convict <-  dcast(dept_conviction_rate2, department ~ conviction) %>% clean_names()

dcast_convict$yes[is.na(dcast_convict$yes)] <-  0
dcast_convict$no[is.na(dcast_convict$no)] <-  0
dcast_convict$case_still_pending[is.na(dcast_convict$case_still_pending)] <-  0
dcast_convict$cannot_determine[is.na(dcast_convict$cannot_determine)] <-  0
dcast_convict$na[is.na(dcast_convict$na)] <-  0

dcast_convict <-  dcast_convict %>% 
  mutate(total= yes+no+case_still_pending+cannot_determine+na,
         pct = yes/total)

dcast_convict$pct_d <- percent_format()(dcast_convict$pct)

dcast_convict <-  dcast_convict %>%  filter(department!='U-Minnesota') %>% 
  mutate(department= case_when(department=='Anoka' ~ 'Anoka County',
                                                                 department=='Itasca' ~' Itasca County',
                                                                 TRUE ~ department))

dcast_convict %>% 
  arrange(desc(pct)) %>% 
  select(department, convictions=yes, totalcases=total, convict_rate=pct_d) %>% 
    kable("html") %>% 
     kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")



```







# Sent for prosecution by department


```{r prosecutebydept, echo=FALSE}


rape%>%tabyl(department_collapse, sentforprosecution)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")



```

##Victim involvement - prosecution

```{r}
rape%>% tabyl(victiminvolve, sentforprosecution)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



##Victim interview
Percentage of cases where victim is interviewed by investigator

```{r victiminterview, echo=FALSE}
victim_int_pct <- rape %>% group_by(victiminterviewed) %>% summarise(count=n()) %>% mutate(pct=count/sum(count)) %>% arrange(desc(count))

victim_int_pct$pct_d <- percent_format()(victim_int_pct$pct)

victim_int_pct %>% select(victiminterviewed, count, pct_d) %>% kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



#Cases investigated, not sent for prosecution
Victim involvement by police actions

##Victim interview
Did investigators conduct a forensic interview with victim?

```{r}
rape  %>% filter(group=="Investigated/Not sent for Prosecution") %>% tabyl(victiminvolve, victiminterviewed)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

##Suspect interviewed
Only cases with a named suspect<br>
Did investigators interview the suspect?

```{r}
rape  %>% filter(suspectflag=="Named suspect" | suspectflag=="Partial name", group=="Investigated/Not sent for Prosecution") %>%
  tabyl(victiminvolve,suspectinterviewed)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

##Evidence collection
Only cases with no delay in reporting<br>
Was all potential evidence collected?

```{r}
rape  %>%filter(delay=="no delay", group=="Investigated/Not sent for Prosecution") %>%  tabyl(victiminvolve,evidence2)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


##Interview witnesses
How often potential witnesses were not interviewed


```{r}
rape  %>% filter(group=="Investigated/Not sent for Prosecution") %>%
  tabyl(victiminvolve,potentialwitnesses_notinterviewed)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```







#BUCKETS
Comparing police actions on cases sent for prosecution versus those not sent<br>


##Victim interview

```{r}
rape %>% tabyl(group2, victiminterviewed)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


##Suspect interview
Only cases with named suspect
```{r}
rape %>% filter(suspectflag=='Named suspect') %>% 
  tabyl(group2, suspectinterviewed)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


##Evidence not collected
Only cases without a delay in reporting
```{r}
rape %>% filter(delay=="no delay") %>% 
  tabyl(group2, evidence2)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


##Witnesses not interviewed
```{r}
rape %>% 
  tabyl(group2, witness2)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")

#rape %>% group_by(potentialwitnesses_notinterviewed) %>% summarise(count=n())
```



##Victim involvement


```{r}
rape %>% 
  tabyl(group2, victiminvolve)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```




##Named suspects
How often cases had named suspects (not including partial names or nicknames)

```{r}
rape %>% 
  tabyl(group2, suspectflag)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



##Assigned to investigators
How often cases were assigned to investigators

```{r}
rape %>% 
  tabyl(department, investigatorsassigned)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


#Cases that involve a repeat offender

```{r}
rape %>% filter(`repeat`!="NA") %>%
  tabyl(department_collapse, investigatorsassigned)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

Repeat offender cases - victim interview

```{r}
rape %>% filter(`repeat`!="NA") %>%
  tabyl(department_collapse, victiminterviewed)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

Repeat offender cases - evidence collection

```{r}
rape %>% filter(`repeat`!="NA") %>%
  tabyl(department_collapse, evidence2)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

Repeat offender cases - witness interviews

```{r}
rape %>% filter(`repeat`!="NA") %>%
  tabyl(department_collapse, witness2)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

Repeat offender cases - sent for prosecution


```{r}
rape %>% filter(`repeat`!="NA") %>%
  tabyl(department_collapse, sentforprosecution)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



```{r}

#repeat offender cases not assigned to an investigator
#rape %>% filter(`repeat`!="NA", investigatorsassigned=="No") %>% select(`repeat`,department, conviction, sentforprosecution, suspectinterviewed)
```



Percent of cases involving a repeat offender<br>
sent for prosecution that resulted in conviction


```{r}
rape %>% filter(`repeat`!="NA") %>% 
  tabyl(sentforprosecution, conviction)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



Percent of cases sent for prosecution that resulted in conviction
<br>
Cases that do NOT involve a repeat offender

```{r}
rape %>% filter(is.na(`repeat`), suspectflag=='Named suspect') %>% 
  tabyl(sentforprosecution, conviction)%>%
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")



```




#Was there a pretext call?
Only cases involving named suspect and cooperative victim

```{r}
rape  %>%
  filter(suspectflag=='Named suspect', victiminvolve=='Cooperated throughout') %>% 
  group_by(pretextcall) %>% summarise(count=n()) %>% 	mutate(pct = (count/sum(count))) %>% 
    knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```





#Investigator assigned by department

```{r}
rape %>% tabyl(department, investigatorsassigned) %>% 
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

#Male victims
```{r}
rape %>% group_by(malevictim) %>% summarise(count=n())%>% mutate(pct=count/sum(count)) %>% 
    knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

#Rape exams
```{r}
rape %>% group_by(rapeexam, testingresults) %>% summarise(count=n()) %>% 
    knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



#Rape exam and other physical evidence

```{r}

rape %>% group_by(physicalevidence) %>% summarise(count=n()) %>% mutate(pct=count/sum(count)) %>% 
    knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

#Investigator assigned by physical evidence
Note that cases are more likely to be assigned when there's multiple pieces of physical evidence

```{r}
rape %>% tabyl(physicalevidence, investigatorsassigned) %>% 
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

Minneapolis - physical evidence and investigator assigned
```{r}
rape %>% filter(department=="Minneapolis") %>% tabyl(physicalevidence, investigatorsassigned) %>% 
    adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

#Go to crime scene


```{r}
rape %>% filter(police_scene!='Does not apply') %>% group_by(police_scene) %>% summarise(count=n()) %>% mutate(pct=count/sum(count)) %>% 
    knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```














```{r movetoS3, eval=FALSE, echo=FALSE,  results="hide"}


#rmarkdown::render("rape2018.Rmd")


# specify keys as environment variables

Sys.setenv("AWS_ACCESS_KEY_ID" =  rstudioapi::askForPassword("AWS_ACCESS_KEY_ID"),

           "AWS_SECRET_ACCESS_KEY" = rstudioapi::askForPassword("AWS_SECRET_ACCESS_KEY"))

get_bucket("strib-data-internal")


put_object(file = "rape2018.html", object = "projects/rape/rape2018.html", bucket = "strib-data-internal")

put_object(file = "rape2018.html", object = "projects/rape/rape2018.html", bucket = "strib-data-internal", acl=c("public-read"))


```



