---
title: "Regression analysis"
author: "MaryJo Webster"
date:  "Last updated: `r Sys.Date()`"
output:
  html_document: 
    toc: true
    to_depth: 1
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, cache=FALSE, fig.height = 3, fig.width = 8)


```


```{r, code=readLines("load_clean_data.R"), echo=FALSE, warning=FALSE, message=FALSE}

```



```{r}
#I had help on this from Christina Knudson, a stats professor at St. Thomas
#she works in R


#clean up data
#eliminate records where "sent for prosecution" is unknown
#eliminate records where all of the key independent variable fields are unknown 

rape_regression <- rape %>%  filter(sentforprosecution!="Cannot determine")

rape_regression <-  rape_regression %>% mutate(reg_exclude=case_when(victiminvolve=="Unknown" & victimintoxicated=="Unknown"& casetype=="Unclear"& rapeexam=="Unknown"& legaltype=="Unknown" ~"exclude", TRUE~"include"))

rape_regression <- rape_regression %>% filter(reg_exclude=="include")

```


```{r}
rape %>% tabyl(victiminvolve, victiminterviewed) %>% 
        adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  adorn_ns() %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```



```{r}
#create a new data frame and populate fields with binary values




rape_regression <- 
  rape_regression %>%
  select(sentforprosecution, chargesfiled, victiminvolve, victimintoxicated, victim_affectmemory, delay, casetype, legaltype, rapeexam, suspectflag, department_collapse, vulnerable) %>% 
  mutate(involve=case_when(victiminvolve=='Cooperated throughout'~1, victiminvolve=='Withdrew at some point'~0),
         intox=case_when(victimintoxicated=='Yes'~1, victimintoxicated=='No'~0),
         delay2=case_when(delay=='delay'~1, delay=='no delay'~0),
         stranger=case_when(casetype=='Acquaintance'~0, casetype=='Stranger'~1),
         force=case_when(legaltype=='Force/Threat/Fear' | legaltype=='Both'~1, legaltype=='Incapacitation'~0),
         exam=case_when(rapeexam=='Yes'~1, rapeexam=='No' | rapeexam=='victim refused' | rapeexam=='Not applicable'~0),
         suspect= case_when(suspectflag=='Named suspect'~1, suspectflag=='None' | suspectflag=='Partial name'~0),
         pros=case_when(sentforprosecution=='Yes'~1, TRUE~0))



#involve = victim involved throughout process
#intox =victim was intoxicated/high
#delay2 = reported to police 2 or more days after incident
#stranger = is a stranger rape
#force = force was used
#exam = rape exam was conducted
#suspect = there is a named suspect (excluding partial names)
#pros = case was sent for prosecution (dependent variable)
#department_collapse = Minneapolis, St Paul, All other (use as controlling variable)




```



```{r}
model <-  glm(pros ~ involve+delay2+suspect, data=rape_regression, family=binomial())

summary(model)
```
```{r}
#victim involvement

exp(3.454)
```

The odds of a case being sent for prosecution are 31 times greater if victim cooperates, than when the victim drops out, even after adjusting for other factors such as whether there was a delay in the reporting or if they didn't have a named suspect.




```{r}
#Delay
exp(.06017)
```

The odds of a case being sent for prosecution drop in half if there was a delay in reporting, even after adjusting for other factors such as victim staying involved or if they have a named suspect.





```{r}
#Intoxication+invovlement


model2 <-  glm(pros ~ intox+involve, data=rape_regression, family=binomial())

summary(model2)
```

```{r}
exp(0.1479)
```



```{r}

#Involve-delay-stranger-named suspect
model3 <-  glm(pros ~ involve+delay2+stranger+suspect, data=rape_regression, family=binomial())

summary(model3)
```

```{r}
#Stranger
exp(0.5732)
```
The odds of a case being sent for prosecution are nearly 2 times higher if the perpetrator was a stranger to the victim, when other factors are considered including whether they had a named suspect, if the victim cooperates throughout and if there's no delay in reporting

```{r}
#the conviction rate is higher for stranger cases than acquaintannce cases when
#they have a named suspect, victim is involved and no delay in reporting

rape %>% filter(suspectflag=='Named suspect', victiminvolve=='Cooperated throughout', delay=='no delay') %>% group_by(casetype, sentforprosecution) %>% summarise(count=n())
```

```{r}

#But if I take suspect out of the variables, I get a very different result
#where stranger cases are less likely to go to prosecution
model4 <-  glm(pros ~ involve+delay2+stranger, data=rape_regression, family=binomial())

summary(model4)
```

```{r}
#Stranger
exp(-0.6302)
```
```{r}

#This model uses just victim involvement and stranger vs acquaintance

model5 <-  glm(pros ~ involve+stranger, data=rape_regression, family=binomial())

summary(model5)
```
```{r}
exp(0.4411)
```

The odds of a stranger case being sent for prosecution are lower than the odds of an acquaintance case, even if the victim cooperates throughout (not taking into consideration whether they have a named suspect or not).








```{r}
rape %>% group_by(chargesfiled) %>% summarise(count=n())
```



```{r}
rape_reg_2 <- rape %>%  filter(chargesfiled=='Yes' | chargesfiled=='No')

rape_reg_2<-  rape_reg_2 %>% mutate(reg_exclude=case_when(victiminvolve=="Unknown" & victimintoxicated=="Unknown"& casetype=="Unclear"& rapeexam=="Unknown"& legaltype=="Unknown" ~"exclude", TRUE~"include"))

rape_reg_2 <- rape_reg_2 %>% filter(reg_exclude=="include")



rape_reg_2 <- 
  rape_reg_2 %>%
  select(sentforprosecution, chargesfiled, victiminvolve, victimintoxicated, victim_affectmemory, delay, casetype, legaltype, rapeexam, suspectflag, department_collapse, vulnerable) %>% 
  mutate(involve=case_when(victiminvolve=='Cooperated throughout'~1, victiminvolve=='Withdrew at some point'~0),
         intox=case_when(victimintoxicated=='Yes'~1, victimintoxicated=='No'~0),
         delay2=case_when(delay=='delay'~1, delay=='no delay'~0),
         stranger=case_when(casetype=='Acquaintance'~0, casetype=='Stranger'~1),
         force=case_when(legaltype=='Force/Threat/Fear' | legaltype=='Both'~1, legaltype=='Incapacitation'~0),
         exam=case_when(rapeexam=='Yes'~1, rapeexam=='No' | rapeexam=='victim refused' | rapeexam=='Not applicable'~0),
         suspect= case_when(suspectflag=='Named suspect'~1, suspectflag=='None' | suspectflag=='Partial name'~0),
         charge=case_when(chargesfiled=='Yes'~1, TRUE~0))
```


```{r}
#Involve-delay-stranger-named suspect
model_charges_v1 <-  glm(charge ~ involve+delay2+stranger+suspect, data=rape_reg_2, family=binomial())

summary(model_charges_v1)
```

The odds of charges being filed are 25 times greater if the victim cooperates throughout the case, even after accounting for other factors such as victim involvement, whether they have a named suspect and whether there was a delay in reporting the case.

```{r}
#
exp(3.2205)
```
The odds of charges being filed are nearly 4 times greater if the perpetrator was a stranger to the victim, even after accounting for other factors such as victim involvement, whether they have a named suspect and whether there was a delay in reporting the case.
```{r}

exp(1.3089)
```
```{r}
model_charges_v2 <-  glm(charge ~ involve+delay2+stranger+suspect+intox, data=rape_reg_2, family=binomial())

summary(model_charges_v2)
```



```{r}
exp(0.3096)



```




```{r}

#Model only using involvement and intoxication, with charges filed as dependent
model_charges_v3 <-  glm(charge ~ involve+intox, data=rape_reg_2, family=binomial())

summary(model_charges_v3)
```

The odds of charges being filed in a case are nearly two times larger if the victim was not intoxicated than if she was intoxicated, even after taking into consideration whether the victim cooperated with the investigation or not.

```{r}
exp(0.5803)


```

```{r}

```



```{r}
model_charges_v4 <-  glm(charge ~ intox, data=rape_reg_2, family=binomial())

summary(model_charges_v4)
```

```{r}
exp(0.6939)
```

