---
title: "Analysis of random sample"
author: "MaryJo Webster, Brandon Stahl, Jennifer Bjorhus"
date:  "Last updated: `r Sys.Date()`"
output:
  html_document: 
    #toc: true
    #to_depth: 1
    #toc_float: true
    theme: flatly
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, cache=FALSE, fig.height = 3, fig.width = 8)

#URL FOR THIS PAGE: http://strib-data-public.s3-us-west-1.amazonaws.com/projects/rape/sample.html
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# load required packages
library(readr) #importing csv files
library(dplyr) #general analysis 
library(ggplot2) #making charts
library(lubridate) #date functions
library(reshape2) #use this for melt function to create one record for each team
library(tidyr)
library(janitor) #use this for doing crosstabs
library(scales) #needed for stacked bar chart axis labels
library(knitr) #needed for making tables in markdown page
#library(car)
library(aws.s3)
library(htmltools)#this is needed for Rstudio to display kable and other html code
library(rmarkdown)
library(readxl)
library(DT) #needed for making  searchable sortable data tble
library(kableExtra)
library(ggthemes)





```




```{r, code=readLines("load_clean_data.R"), echo=FALSE, warning=FALSE, message=FALSE}
#need this for loading main data
```


```{r}

#break apart big table into all others, Mpls and St Paul
rape_allOthers <-  rape %>% filter(top2=='All others')
rape_mpls <-  rape %>% filter(department=='Minneapolis')
rape_stpaul <-  rape %>% filter(department=='St. Paul')

#Create random samples of Minneapolis and St Paul (about half the cases for each)
rape_sample_mpls <- sample_n(rape_mpls, 200)
rape_sample_stpaul <- sample_n(rape_stpaul, 120)


#Merge the 3 files together
rape_sample <- rbind(rape_sample_mpls, rape_sample_stpaul, rape_allOthers)
```


#Cases included

<p>This analysis is of a random sample of about half the cases from Minneapolis, plus all the cases from other agencies that we requested data from. Here are the number of cases included from each department. This is in order to downplay the influence of the large share of Mpls cases</p>
```{r}
rape_sample %>%
  group_by(department) %>%
  summarise(Number_cases=n()) %>%
  arrange(desc(Number_cases)) %>%
  rename(dept=department)%>%
  adorn_totals("row") %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")



```
<br>

#Analysis results

##Assigned to investigators

```{r}
investigate <- rape_sample %>% group_by(investigatorsassigned) %>%
  summarise(count=n()) %>% 
	mutate(pct = count/sum(count)) %>% 
  filter(investigatorsassigned=="Yes" | investigatorsassigned=="No")


investigate_chart <- 	ggplot(investigate, aes(x = investigatorsassigned, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((investigate$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Percentage of cases assigned to investigator",
       x=NULL,
       y=NULL)

plot(investigate_chart)
```



##Percent of cases sent for prosecution
<p>Only about 1 in four cases is sent for prosecution. Among the remainder, some aren't even assigned to investigators.</p>
```{r}



buckets <- rape_sample %>% group_by(group2) %>%
  summarise(count=n()) %>% 
	mutate(pct = count/sum(count)) %>% 
  filter(group2!="NA")


buckets_chart <- 	ggplot(buckets, aes(x = group2, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((buckets$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = NULL,
       x=NULL,
       y=NULL)

plot(buckets_chart)


```

<br>
<br>

##Percent of cases where charges were filed
<br>
<br>
```{r}

charges <-  rape_sample %>% group_by( chargesfiled) %>% summarise(count=n()) %>% 
	mutate(pct = (count/sum(count))) %>%  
filter(chargesfiled=="Yes" | chargesfiled=="No"| chargesfiled=="Cannot determine")

charges_chart <- 	ggplot(charges, aes(x = chargesfiled, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((charges$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = NULL,
       x=NULL,
       y=NULL)

plot(charges_chart)
```

<br>

<br>

##Percent of cases resulting in conviction
<p>Less than 1 in 10 of the cases we reviewed resulted in conviction.</p>
```{r}




convict <-  rape_sample %>% group_by( conviction) %>% summarise(count=n()) %>% 
	mutate(pct = (count/sum(count))) %>% 
  filter(conviction=="Yes" | conviction=="No"| conviction=="Cannot determine")

convict_chart <- 	ggplot(convict, aes(x = conviction, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((convict$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = NULL,
       x=NULL,
       y=NULL)

plot(convict_chart)


```
<br>
<br>
<hr>

#Case investigations
<p>The charts below look at how often investigators took basic policing steps in the cases we reviewed.</p>
<br>
<p>A recommended best practice is for investigators to conduct a more thorough interview after the victim makes an initial report to the officer responding to the initial call.</p>

```{r}




int <-  rape_sample %>% group_by(victiminterviewed) %>% summarise(count=n()) %>% mutate(pct = (count/sum(count))) %>% 
  filter(victiminterviewed=="No" | victiminterviewed=="Yes" | victiminterviewed=="Attempted")


int_chart <- 	ggplot(int, aes(x = victiminterviewed, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", nudge_x=0, nudge_y=-.05,label=paste0(round((int$pct)*100,0),"%"))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
 # theme(axis.text.y=element_blank())+
  labs(title = "Did investigators interview the victim?",
       x=NULL,
       y=NULL)

plot(int_chart)

```






<br>
<br>

<p>About 70% of the cases we reviewed listed one or more suspect names in the report, yet investigators failed to interview that person more often than not.</p>
```{r}


int_suspect <-  rape_sample %>% filter(suspectflag=="Named suspect") %>% group_by(suspectinterviewed) %>% summarise(count=n()) %>% mutate(pct = (count/sum(count))) %>% 
  filter(suspectinterviewed=="No"| suspectinterviewed=="Yes" | suspectinterviewed=="Attempted")



int_suspect_chart <- 	ggplot(int_suspect, aes(x = suspectinterviewed, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", nudge_x=0, nudge_y=-.03,label=paste0(round((int_suspect$pct)*100,0),"%"))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
   #theme(axis.text.y=element_blank())+
  labs(title = "Did investigators interview named suspects?",
       subtitle="Only cases with named suspect",
       x=NULL,
       y=NULL)

plot(int_suspect_chart)
```

<br>
<br>

<p>When reviewing cases, we looked for indications of evidence that could've been collected but there was no documentation in the report that it was. This might have included DNA, clothing or bed sheets, surveillance video or cell phone data.</p>
```{r}
evidence <-  rape_sample %>% filter(delay=="no delay") %>% group_by(evidence2) %>% summarise(count=n()) %>% 	mutate(pct = (count/sum(count)))


evidence_chart <- 	ggplot(evidence, aes(x = evidence2, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", nudge_x=0, nudge_y=-.05,label=paste0(round((evidence$pct)*100,0),"%"))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
     #theme(axis.text.y=element_blank())+
  labs(title = "Did investigators collect all potential evidence?",
       subtitle="Only cases with no reporting delay",
       x=NULL,
       y=NULL)

plot(evidence_chart)
```

<br>
<br>


```{r}
witness <-  rape_sample  %>% group_by(witness2) %>% summarise(count=n()) %>% 	mutate(pct = (count/sum(count))) 


witness_chart <- 	ggplot(witness, aes(x = witness2, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", nudge_x=0, nudge_y=-.05,label=paste0(round((witness$pct)*100,0),"%"))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
      #theme(axis.text.y=element_blank())+
  labs(title = "Did investigators interview all potential witnesses?",
             x=NULL,
       y=NULL)

plot(witness_chart)
```
<br>
<br>
<hr>

#Cases not sent for prosecution
<p>The Star Tribune wanted to understand what went wrong with the 3 out of 4 cases that were never sent to prosecutors. Looking at just those 600 cases, we found police were even less likely to take the most basic investigatory steps.</p>
<br>

```{r}
int_np <-  rape_sample %>% group_by(group2, victiminterviewed) %>% summarise(count=n())

int_np <-  int_np %>% mutate(pct = (count/sum(count))) %>% 
  filter(victiminterviewed=="No"| victiminterviewed=="Yes" | victiminterviewed=="Attempted" , group2=="Not sent for prosecution")


int_np_chart <- 	ggplot(int_np, aes(x = victiminterviewed, y = pct)) +
	geom_col(color="#A8B9C5", fill="#A8B9C5") +
  coord_flip()+
  geom_text(stat="identity", nudge_x=0, nudge_y=-.15,label=paste0(round((int_np$pct)*100,0),"%"))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
 # theme(axis.text.y=element_blank())+
  labs(title = "Did investigators interview the victim?",
       subtitle="Cases not sent to prosecutors",
       x=NULL,
       y=NULL)

plot(int_np_chart)

```
<br>
<br>

```{r}

int_suspect_np <-  rape_sample %>% filter(suspectflag=="Named suspect") %>% group_by(group2, suspectinterviewed) %>% summarise(count=n())

int_suspect_np <-  int_suspect_np %>% mutate(pct = (count/sum(count))) %>% 
  filter(suspectinterviewed=="No"| suspectinterviewed=="Yes" | suspectinterviewed=="Attempted", group2=="Not sent for prosecution")



int_suspect_np_chart <- 	ggplot(int_suspect_np, aes(x = suspectinterviewed, y = pct)) +
	geom_col(color="#A8B9C5", fill="#A8B9C5") +
  coord_flip()+
  geom_text(stat="identity", nudge_x=0, nudge_y=-.025,label=paste0(round((int_suspect_np$pct)*100,0),"%"))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
   #theme(axis.text.y=element_blank())+
  labs(title = "Did investigators interivew a named suspect?",
       subtitle="Cases not sent to prosecutors",
       x=NULL,
       y=NULL)

plot(int_suspect_np_chart)
```

<br>
<br>

```{r}
evidence_np <-  rape_sample %>% filter(delay=="no delay") %>% group_by(group2, evidence2) %>% summarise(count=n()) 
  
  evidence_np <-  evidence_np %>% mutate(pct = (count/sum(count)))	%>%
	filter(group2=="Not sent for prosecution")


evidence_np_chart <- 	ggplot(evidence_np, aes(x = evidence2, y = pct)) +
	geom_col(color="#A8B9C5", fill="#A8B9C5") +
  coord_flip()+
  geom_text(stat="identity", nudge_x=0, nudge_y=-.1,label=paste0(round((evidence_np$pct)*100,0),"%"))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
     #theme(axis.text.y=element_blank())+
  labs(title = "Did investigators collect all potential evidence listed in report?",
       subtitle="Cases not sent to prosecutors; no reporting delay",
       x=NULL,
       y=NULL)

plot(evidence_np_chart)
```

<br>
<br>

```{r}
witness_np <-  rape_sample  %>% group_by(group2, witness2) %>% summarise(count=n()) 

witness_np <-  witness_np %>% 	mutate(pct = (count/sum(count))) %>% 
filter(group2=="Not sent for prosecution")


witness_np_chart <- 	ggplot(witness_np, aes(x = witness2, y = pct)) +
	geom_col(color="#A8B9C5", fill="#A8B9C5") +
  coord_flip()+
  geom_text(stat="identity", nudge_x=0, nudge_y=-.05,label=paste0(round((witness_np$pct)*100,0),"%"))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
      #theme(axis.text.y=element_blank())+
  labs(title = "Did investigators interview all potential witnesses?",
       subtitle="Cases not sent to prosecutors",
             x=NULL,
       y=NULL)

plot(witness_np_chart)
```
<br>
<br>
<hr>


#Victim involvement

<p>About one-third of victims either choose to no longer cooperate in an investigation or police are unable to reach them later in the investigation.</p>
<br>
```{r}
involve <-  rape_sample %>% 
  group_by(victiminvolve) %>%
  summarise(count=n()) %>% 
  mutate(pct = (count/sum(count)))



involve_chart <- 	ggplot(involve, aes(x = victiminvolve, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((involve$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = NULL,
       x=NULL,
       y=NULL)

plot(involve_chart)
```


<br>
<br>

<p>When a victim stays involved in the investigation, the case is far more likely to be sent to prosecutors.</p>
```{r}
involve_prosecution <-  rape_sample %>% 
  group_by(group2, victiminvolve) %>%
  summarise(count=n()) 


involve_prosecution <-involve_prosecution %>% group_by(victiminvolve) %>% 
  mutate(pct = (count/sum(count))) %>% 
    filter(group2=="Sent for prosecution")

involve_prosecution <-  involve_prosecution %>% filter(victiminvolve=="Withdrew at some point" | victiminvolve=="Cooperated throughout")


involve_prosecution_chart <- 	ggplot(involve_prosecution, aes(x = victiminvolve, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((involve_prosecution$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Percent sent for prosecution",
       subtitle="By victim involvement",
       x=NULL,
       y=NULL)

plot(involve_prosecution_chart)
```

<br>
<br>

<p>And we've only found 1 case that resulted in a conviction after the victim dropped out.</p>
```{r}
involve_conviction <-  rape_sample %>% 
  group_by(conviction, victiminvolve) %>%
  summarise(count=n()) 


involve_conviction <-involve_conviction %>% group_by(victiminvolve) %>% 
  mutate(pct = (count/sum(count))) %>% 
    filter(conviction=="Yes")

involve_conviction <-  involve_conviction %>% filter(victiminvolve=="Withdrew at some point" | victiminvolve=="Cooperated throughout")


involve_conviction_chart <- 	ggplot(involve_conviction, aes(x = victiminvolve, y = pct)) +
	geom_col(color="#556E7F", fill="#556E7F") +
  coord_flip()+
  geom_text(stat="identity", label=paste0(round((involve_conviction$pct)*100,0),"%"), hjust= -0.5, size=4, position= position_dodge(width=1))+
	scale_y_continuous(labels = percent, limits=c(0,1))+
  theme_hc()+
  labs(title = "Share of cases resulting in conviction",
       subtitle="By victim involvement",
       x=NULL,
       y=NULL)

plot(involve_conviction_chart)


```

