---
title: "Alternative analysis using 3 buckets"
subtitle: "Internal only"
author: "MaryJo Webster"
date:  "Last updated: `r Sys.Date()`"
output:
  html_document: 
    toc: true
    to_depth: 1
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE)

#URL FOR THIS PAGE: http://strib-data-internal.s3-us-west-1.amazonaws.com/projects/rape/threebuckets.html
```



```{r, code=readLines("load_clean_data.R"), echo=FALSE, warning=FALSE, message=FALSE}

```


#BUCKETS
Cases split into 3 groups

```{r}

#The field called "group" is created in the load_clean_data script
#It creates 3 buckets of cases -- those that were not assigned to investigators, those that were assigned and investigated but not sent for prosecution and those that were investigated and sent for prosecution. 


grouptotals <- rape %>% 
  group_by(group) %>%
  summarise(count=n()) %>%
  mutate(pct=count/sum(count)) %>% 
  arrange(desc(pct))

grouptotals$pct_d <-  percent_format()(grouptotals$pct)

grouptotals %>% select(group, count, pct_d) %>% kable("html") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")

```

##Victim interview
Did investigators conduct a forensic interview with victim?

```{r}
rape  %>% tabyl(group, victiminterviewed)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

##Suspect interviewed
Only cases with a named suspect<br>
Did investigators interview the suspect?

```{r}
rape  %>% filter(suspectflag=="Named suspect" | suspectflag=="Partial name") %>%
  tabyl(group,suspectinterviewed)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

##Evidence collection
Only cases with no delay in reporting<br>
Was all potential evidence collected?

```{r}
rape  %>%filter(delay=="no delay") %>%  tabyl(group,potentialevidence_notcollected)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


##Interview witnesses
Were all potential witnesses interviewed?


```{r}
rape  %>% tabyl(group,potentialwitnesses_notinterviewed)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

##Visit scene
Did investigators visit crime scene, where applicable?


```{r}
rape  %>% filter(police_scene!="Does not apply") %>%  tabyl(group,police_scene)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```


##Victim involvement
Did victim stick with the case?

```{r}
rape  %>% tabyl(group,victiminvolve)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```

##Named suspect
How often was there a named suspct?


```{r}
rape  %>%  tabyl(group,suspectflag)%>%
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(rounding = "half up", digits=0) %>% 
  adorn_title("top")%>%
  knitr::kable("html") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position="left")
```




```{r movetoS3, echo=FALSE, eval=FALSE, results="hide"}

#testing


# specify keys as environment variables

Sys.setenv("AWS_ACCESS_KEY_ID" =  rstudioapi::askForPassword("AWS_ACCESS_KEY_ID"),

           "AWS_SECRET_ACCESS_KEY" = rstudioapi::askForPassword("AWS_SECRET_ACCESS_KEY"))

get_bucket("strib-data-internal")


put_object(file = "threebuckets.html", object = "projects/rape/threebuckets.html", bucket = "strib-data-internal")

put_object(file = "threebuckets.html", object = "projects/rape/threebuckets.html", bucket = "strib-data-internal", acl=c("public-read"))


```
